\papertitle

### 2025-05-13 paper/main.tex
update statement

\begin{figure*}[bt!]
    \centering
    \includegraphics[width=1.0\textwidth]{fig_workflow_larger_font.jpg}
    \caption{Detailed model workflow.}\label{fig:workflow}
\end{figure*}

@@

The code and data that support the findings of this study are available at [REDACTED]. Google's terms of use forbid publicly redistributing their data: for reproducibility purposes, those training data are available directly from the authors upon request. [Reviewers: please use this anonymized URL for your review: https://figshare.com/s/0acd076b1a11286ff3e4 We have submitted the training data file separately to the journal as supplementary material for review only, to abide by the terms of use.]
%https://github.com/gboeing/travel-time-prediction

>>>>

\begin{figure*}[bt!]
    \centering
    \includegraphics[width=1.0\textwidth]{fig_workflow.jpg}
    \caption{Detailed model workflow.}\label{fig:workflow}
\end{figure*}

@@

The code and data that support the findings of this study are available at [REDACTED], minus one training data file which Google's terms of use forbid publicly redistributing. For replication purposes, data equivalent to those in that file are freely available (up to a monthly usage quota) directly from the Google Routes API (\url{https://developers.google.com/maps/documentation/routes}) by signing up for an API key from the Google Cloud Console (\url{https://console.cloud.google.com/}).
%\url{https://github.com/gboeing/travel-time-prediction}

[Reviewers: please use this anonymized URL for your review instead: \url{https://figshare.com/s/0acd076b1a11286ff3e4}. We have submitted the original training data file separately to the journal directly as supplementary material for review only, to abide by the terms of use.]
